Individual and Differential Harm in Redistricting

### 2025-07-30 paper/figures/corr_table.tex
cut lots

\begin{tabular}[t]{l>{}r>{}r>{}r>{}r>{}r}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Correlation with differential harm and:} \\
\cmidrule(l{3pt}r{3pt}){2-6}
State & Exp. Dem. seats & Efficiency gap & Partisan bias & Mean-median & Declination\\
\midrule
Utah & \cellcolor[HTML]{8A671F}{-0.983} & \cellcolor[HTML]{75689E}{0.957} & \cellcolor[HTML]{927421}{-0.893} & \cellcolor[HTML]{8E6C20}{-0.945} & \cellcolor[HTML]{947722}{-0.876}\\
Mississippi & \cellcolor[HTML]{9D8627}{-0.772} & \cellcolor[HTML]{BFD9D5}{0.207} & \cellcolor[HTML]{E8EEE3}{0.031} & \cellcolor[HTML]{E7E5C0}{-0.096} & \cellcolor[HTML]{A89735}{-0.656}\\
Iowa & \cellcolor[HTML]{AD9F3D}{-0.597} & \cellcolor[HTML]{A0B5C2}{0.449} & \cellcolor[HTML]{DED99D}{-0.185} & \cellcolor[HTML]{C4DCD7}{0.184} & \cellcolor[HTML]{A9C2C9}{0.365}\\
North Carolina & \cellcolor[HTML]{8E6C20}{-0.943} & \cellcolor[HTML]{8A88AE}{0.740} & \cellcolor[HTML]{9AAABC}{0.520} & \cellcolor[HTML]{8C8DB0}{0.704} & \cellcolor[HTML]{9BAABC}{0.519}\\
Wisconsin & \cellcolor[HTML]{998024}{-0.816} & \cellcolor[HTML]{929BB4}{0.621} & \cellcolor[HTML]{C2DBD7}{0.191} & \cellcolor[HTML]{9096B2}{0.652} & \cellcolor[HTML]{A8C1C8}{0.374}\\
New Jersey & \cellcolor[HTML]{9B8425}{-0.789} & \cellcolor[HTML]{9FB4C1}{0.459} & \cellcolor[HTML]{DCE8DF}{0.082} & \cellcolor[HTML]{EEF0E0}{-0.014} & \cellcolor[HTML]{A7C0C7}{0.381}\\
Massachusetts & \cellcolor[HTML]{987E23}{-0.826} & \cellcolor[HTML]{E9E9CA}{-0.069} & \cellcolor[HTML]{E1DDA7}{-0.158} & \cellcolor[HTML]{CADFD9}{0.159} & \cellcolor[HTML]{808080}{NA}\\
California & \cellcolor[HTML]{AEA03E}{-0.590} & \cellcolor[HTML]{939BB4}{0.616} & \cellcolor[HTML]{DCD798}{-0.199} & \cellcolor[HTML]{D1C97B}{-0.302} & \cellcolor[HTML]{AAC3C9}{0.359}\\
\bottomrule
\end{tabular}

>>>>

\begin{tabular}[t]{l>{}r>{}r>{}r>{}r>{}r}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Correlation with differential harm and:} \\
\cmidrule(l{3pt}r{3pt}){2-6}
State & Exp. Dem. seats & Efficiency gap & Partisan bias & Mean-median & Declination\\
\midrule
Utah & \cellcolor[HTML]{8A671F}{$-0.983$} & \cellcolor[HTML]{75689E}{$0.957$} & \cellcolor[HTML]{927421}{$-0.893$} & \cellcolor[HTML]{8E6C20}{$-0.945$} & \cellcolor[HTML]{947722}{$-0.876$}\\
Mississippi & \cellcolor[HTML]{9D8627}{$-0.772$} & \cellcolor[HTML]{BFD9D5}{$0.207$} & \cellcolor[HTML]{E8EEE3}{$0.031$} & \cellcolor[HTML]{E7E5C0}{$-0.096$} & \cellcolor[HTML]{A89735}{$-0.656$}\\
Iowa & \cellcolor[HTML]{AD9F3D}{$-0.597$} & \cellcolor[HTML]{A0B5C2}{$0.449$} & \cellcolor[HTML]{DED99D}{$-0.185$} & \cellcolor[HTML]{C4DCD7}{$0.184$} & \cellcolor[HTML]{A9C2C9}{$0.365$}\\
North Carolina & \cellcolor[HTML]{8E6C20}{$-0.943$} & \cellcolor[HTML]{8A88AE}{$0.740$} & \cellcolor[HTML]{9AAABC}{$0.520$} & \cellcolor[HTML]{8C8DB0}{$0.704$} & \cellcolor[HTML]{9BAABC}{$0.519$}\\
Wisconsin & \cellcolor[HTML]{998024}{$-0.816$} & \cellcolor[HTML]{929BB4}{$0.621$} & \cellcolor[HTML]{C2DBD7}{$0.191$} & \cellcolor[HTML]{9096B2}{$0.652$} & \cellcolor[HTML]{A8C1C8}{$0.374$}\\
New Jersey & \cellcolor[HTML]{9B8425}{$-0.789$} & \cellcolor[HTML]{9FB4C1}{$0.459$} & \cellcolor[HTML]{DCE8DF}{$0.082$} & \cellcolor[HTML]{EEF0E0}{$-0.014$} & \cellcolor[HTML]{A7C0C7}{$0.381$}\\
Massachusetts & \cellcolor[HTML]{987E23}{$-0.826$} & \cellcolor[HTML]{E9E9CA}{$-0.069$} & \cellcolor[HTML]{E1DDA7}{$-0.158$} & \cellcolor[HTML]{CADFD9}{$0.159$} & \cellcolor[HTML]{808080}{NA}\\
California & \cellcolor[HTML]{AEA03E}{$-0.590$} & \cellcolor[HTML]{939BB4}{$0.616$} & \cellcolor[HTML]{DCD798}{$-0.199$} & \cellcolor[HTML]{D1C97B}{$-0.302$} & \cellcolor[HTML]{AAC3C9}{$0.359$}\\
\bottomrule
\end{tabular}
